Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-03 phaseDelay.tex
Updates from ShareLaTeX

\begin{figure}[!t] 
 \renewcommand{\baselinestretch}{0.7}
 \scriptsize
\begin{center}
\begin{tabular}{r@{~}|r@{~}r@{~}r|@{~}l@{~}l|@{~}r@{~}l}  % I attach your cursor. thrust, parry, yo!
  \multicolumn{1}{c}{~} &\multicolumn{3}{c}{Percentiles}&\multicolumn{2}{l}{~~~~~~Phase}\\\cline2-6}
N & 25th & 50th & 75th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline
\\
 48&   14&   30&   51&Before&DesignInspect &1.00 & **********  \\
 53&   13&   28&   49&Before&CodeReview &0.93 & **********  \\
 94&   22&   45&   80&Before&CodeInspect &1.50 & ***************  \\
153&   38&   77&  130&Before&UnitTest &2.56 & **************************  \\
127&   30&   65&  128&Before&IntTest &2.16 & **********************  \\
 92&   24&   56&   89&Before&SysTest &1.86 & *******************  \\

>>>>

\begin{figure}[!t] 
 \renewcommand{\baselinestretch}{0.7}
 \scriptsize
\begin{center}
\begin{tabular}{r@{~}|r@{~}r@{~}r|@{~}l@{~}l|@{~}r@{~}l}  % I attach your cursor. thrust, parry, yo!
  \multicolumn{1}{c}{~} &\multicolumn{3}{c}{Percentiles}&\multicolumn{2}{l}{~~~~~~Phase}\\%\cline{2-6}
N & 25th & 50th & 75th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline
\\
 48&   14&   30&   51&Before&DesignInspect &1.00 & **********  \\
 53&   13&   28&   49&Before&CodeReview &0.93 & **********  \\
 94&   22&   45&   80&Before&CodeInspect &1.50 & ***************  \\
153&   38&   77&  130&Before&UnitTest &2.56 & **************************  \\
127&   30&   65&  128&Before&IntTest &2.16 & **********************  \\
 92&   24&   56&   89&Before&SysTest &1.86 & *******************  \\
